\documentclass[../Moduli_Spaces_of_Riemann_Surfaces.tex]{subfiles}
\begin{document}
    \section{Moduli Space of $T^2$}\label{MS:sec:moduli_space_torus}
    We show that the moduli space of the torus $T^2$ is $\H/\!\PSL{2}{\Z}$, where $\H$ is the upper-half plane of $\C$ and $\PSL{2}{\Z}\coloneqq\SL_2\!\l(\Z\r)\!/\!\l\{\pm I\r\}$ is the \textit{modular group}, which acts on $\H$ via
    \begin{equation*}
        \begin{pmatrix}
            a & b \\
            c & d
        \end{pmatrix}\tau\coloneqq\frac{a\tau+b}{c\tau+d}.
    \end{equation*}
    We first need a technical lemma, which gives an equivalent condition for a biholomorphism between tori in terms of their lattices.
    \begin{lemma}\label{MS:lem:moduli_space_torus_1}
        Let $\Gamma,\Gamma'\subseteq\C$ be two lattices and suppose $\alpha\Gamma\subseteq\Gamma'$ for some $\alpha\in\C^\ast$. Then $z\mapsto\alpha z$ descends to a holomorphic map $\phi:\C/\Gamma\to\C/\Gamma'$, which is biholomorphic iff $\alpha\Gamma=\Gamma'$.
    \end{lemma}
    \begin{proof}
        Let $\Gamma\coloneqq\Z\omega_1\oplus\Z\omega_2$ and $\Gamma'\coloneqq\Z\omega_1'\oplus\Z\omega_2'$. Define $\phi\l(z+\Gamma\r)\coloneqq\alpha z+\Gamma'$ for all $z\in\C$, which is clearly holomorphic if it is well-defined in the first place. Indeed, take $z_1,z_2\in\C$ such that $z_1+\Gamma=z_2+\Gamma$. Then $z_1-z_2\in\Gamma$, so $z_1-z_2=m\omega_1+n\omega_2$ for some $n,m\in\Z$. Observe that
        \begin{equation*}
            \alpha z_1-\alpha z_2=\alpha\l(z_1-z_2\r)=m\l(\alpha\omega_1\r)+n\l(\alpha\omega_2\r)\in\alpha\Gamma\subseteq\Gamma',
        \end{equation*}
        so $\alpha z_1+\Gamma'=\alpha z_2+\Gamma'$. This shows that $\phi$ is well-defined. Furthermore, it is invertible with holomorphic inverse $\phi^{-1}\!\l(z+\Gamma'\r)\coloneqq z/\alpha+\Gamma$ iff $\phi^{-1}$ is well-defined, in which case $\phi$ is a biholomorphism. We claim that this occurs iff $\alpha\Gamma=\Gamma'$.
        \begin{itemize}
            \item ($\Rightarrow$): It suffices to show that $\Gamma'\subseteq\alpha\Gamma$, so take $m\omega_1'+n\omega_2'\in\Gamma'$. Then $\phi^{-1}\!\l(m\omega_1'+n\omega_2'+\Gamma'\r)=\l(m\omega_1'+n\omega_2'\r)\!/\alpha+\Gamma$, but since $m\omega_1'+n\omega_2'+\Gamma'=0+\Gamma'$ and $\phi^{-1}\!\l(0+\Gamma'\r)=0+\Gamma$, we see that $\l(m\omega_1'+n\omega_2'\r)\!/\alpha\in\Gamma$.
                \vspace{-0.05in}
            \item ($\Leftarrow$): Take $z_1,z_2\in\C$ such that $z_1+\Gamma'=z_2+\Gamma'$, so $z_1-z_2\in\Gamma'\subseteq\alpha\Gamma$ and hence $z_1/\alpha-z_2/\alpha=\l(z_1-z_2\r)\!/\alpha\in\Gamma$. Then $z_1/\alpha+\Gamma=z_2/\alpha+\Gamma$, so $\phi^{-1}$ is well-defined.\qed
        \end{itemize}
    \end{proof}
    \begin{lemma}\label{MS:lem:moduli_space_torus_2}
        Any torus $\C/\Gamma$ is biholomorphic to $X_\tau\!\coloneqq\C/\!\l(\Z+\tau\Z\r)$ for some $\tau\in\H$.
    \end{lemma}
    \begin{remark}
        Intuitively, scaling and rotating the lattice, which are biholomorphisms of the plane, should preserve the complex structure on the torus. Thus only one complex parameter is needed to generate the torus, which we choose to be the ratio $\tau\coloneqq\omega_2/\omega_1$.\exqed
    \end{remark}
    \begin{proof}
        Let $\Gamma\coloneqq\Z\omega_1\oplus\Z\omega_2$ and set $\alpha\coloneqq1/\omega_1$ and $\tau\coloneqq\omega_2/\omega_1$. Then $\Im\tau\neq0$, lest $\omega_1,\omega_2$ be linearly dependent over $\R$. Without loss of generality, suppose that $\Im\tau>0$; if not, take $\tau\coloneqq\bar{\omega_2}/\omega_1$. Then, since
        \begin{equation*}
            \alpha\l(m\omega_1+n\omega_2\r)=\alpha\omega_1\l(m+n\omega_2/\omega_1\r)=m+n\tau
        \end{equation*}
        for all $m,n\in\Z$, we see that $\alpha\Gamma=\Z\oplus\Z\tau$. By Lemma \ref{MS:lem:moduli_space_torus_1}, the map $z\mapsto\alpha z$ descends to a biholomorphism $\phi:\C/\Gamma\to\C/\!\l(\Z\oplus\Z\tau\r)=X_\tau$, so $\C/\Gamma\iso X_\tau$.\qed
    \end{proof}
    \begin{theorem}\label{MS:thm:moduli_space_torus}
        For any $\tau,\tau'\in\H$, the tori $X_{\tau}$ and $X_{\tau'}$ are biholomorphic iff $\tau$ and $\tau'$ lie in the same orbit of the action of $\PSL{2}{\Z}$ on $\H$.
    \end{theorem}
    \begin{corollary}
        The moduli space of $T^2$ is $\H/\!\PSL{2}{\Z}$.
    \end{corollary}
    \begin{proof}
        The backwards direction is relatively straightforward. Indeed, note that
        \begin{equation*}
            \tau'=\frac{a\tau+b}{c\tau+d}\ \ \ \ \ \ \ \ \Rightarrow\ \ \ \ \ \ \ \ \tau=\frac{b-d\tau'}{c\tau'-a}
        \end{equation*}
        for any $a,b,c,d\in\Z$ with $ad-bc=1$. Setting $\Gamma\coloneqq\Z\oplus\Z\tau$ and $\Gamma'\coloneqq\Z\oplus\Z\tau'$, we see with $\alpha\coloneqq c\tau'-a$ that $\alpha\Gamma\subseteq\Gamma'$. We claim that $\alpha\Gamma=\Gamma'$, from which the result follows from Lemma \ref{MS:lem:moduli_space_torus_1}. Indeed, for any $m,n\in\Z$, the condition that $ad-bc=1$ shows that
        \begin{equation*}
            \l(m+n\tau'\r)\!/\alpha=\frac{\l(na-mc\r)\tau+\l(nb-md\r)}{a\l(c\tau+d\r)-c\l(a\tau+b\r)}=\l(nb-md\r)+\l(na-mc\r)\tau\in\Z\oplus\Z\tau,
        \end{equation*}
        so $\Gamma'=\Z\oplus\Z\tau'\subseteq\alpha\l(\Z\oplus\Z\tau\r)\subseteq\alpha\Gamma$. For the forward direction, let $\phi:X_\tau\to X_{\tau'}$ be a biholomorphism. By Proposition \ref{CS:prp:lift_maps}, this biholomorphism lifts to a unique biholomorphism $\widetilde{\phi}:\C\to\C$ fixing $0$ and making the diagram
        \begin{equation*}
            \begin{tikzcd}
                \C \ar[r, "\tilde{\phi}"] \ar[d, "\pi"'] & \C \ar[d, "\pi'"] \\
                \C/\Gamma \ar[r, "\phi"] & \C/\Gamma'
            \end{tikzcd}
        \end{equation*}
        commute. We claim that $\widetilde{\phi}\l(z\r)=\alpha z$ for some $\alpha\in\C^\ast$.\footnote{This is a classical result from complex analysis, which states that every automorphism on $\C$ is of the form $z\mapsto\alpha z+\beta$ for some $\alpha,\beta\in\C$ with $\alpha\neq0$. For a proof, see \cite[][Lemma 2.8]{i&t}. Since our automorphism $\widetilde{\phi}$ is more specific, we present a simpler proof, which roughly follows \cite[][Proposition 1.3.2]{diamond}.} Indeed, fix $\lambda\in\Gamma$ and consider the map $f_\lambda\!\l(z\r)\coloneqq\tilde{\phi}\l(z+\lambda\r)-\tilde{\phi}\l(z\r)$. Then, since $z+\lambda+\Gamma=z+\Gamma$, we see that $\phi\l(z+\lambda+\Gamma\r)=\phi\l(z+\Gamma\r)$ and hence the commutativity of the diagram forces $\tilde{\phi}\l(z+\lambda\r)+\Gamma'=\tilde{\phi}\l(z\r)+\Gamma'$. Thus $f_\lambda\!\l(z\r)\in\Gamma'$ for all $z\in\C$, so, since $f_\lambda$ is a continuous map into a discrete set, it must be constant. Differentiating gives us $f_\lambda'\l(z\r)=\tilde{\phi}'\l(z+\lambda\r)-\tilde{\phi}'\l(z\r)=0$, so $\tilde{\phi}'\l(z+\lambda\r)=\tilde{\phi}'\l(z\r)$ for all $z\in\C$. But $\lambda\in\Gamma$ is arbitrary, so $\tilde{\phi}'$ is $\Gamma$-periodic. Thus $\tilde{\phi}'$ is a bounded entire function and hence is constant by Liouville's Theorem. This shows that $\tilde{\phi}\l(z\r)=\alpha z+\beta$ for some $\alpha,\beta\in\C$ with $\alpha\neq0$, but since $\widetilde{\phi}$ fixes $0$, we have $\widetilde{\phi}\l(z\r)=\alpha z$, as desired. We now claim that $\alpha\Gamma=\Gamma'$.
        \begin{itemize}
            \item Indeed, for all $z\in\alpha\Gamma$, we have $z/\alpha\in\Gamma$ and so $z/\alpha+\Gamma=0+\Gamma$. Applying $\phi$ to both sides and comparing gives
                \begin{equation*}
                    0+\Gamma'=\phi\l(0+\Gamma\r)=\phi\l(z/\alpha+\Gamma\r)=\tilde{\phi}\l(z/\alpha\r)+\Gamma'=z+\Gamma',
                \end{equation*}
                so $z\in\Gamma'$. The converse is similar.
        \end{itemize}
        Observe then that $\tilde{\phi}\l(\tau\r)=\alpha\tau=b-d\tau'$ and $\tilde{\phi}\l(1\r)=\alpha=c\tau'-a$ for some $a,b,c,d\in\Z$, so
        \begin{equation*}
            \tau=\frac{b-d\tau'}{c\tau'-a}\ \ \ \ \ \ \ \ \textrm{and hence}\ \ \ \ \ \ \ \ \tau'=\frac{a\tau+b}{c\tau+d}.
        \end{equation*}
        A computation now shows that $\alpha=-\l(ad-bc\r)/\l(c\tau+d\r)$, so $ad-bc\neq0$. Then, since
        \begin{equation*}
            \begin{pmatrix}
                \alpha\tau \\ \alpha
            \end{pmatrix}=
            \begin{pmatrix}
                b & -d \\
                -a & c
            \end{pmatrix}
            \begin{pmatrix}
                1 \\ \tau'
            \end{pmatrix},
        \end{equation*}
        we solve for $\tau'$ to obtain
        \begin{equation*}
            \tau'=-\frac{b\alpha+a\alpha\tau}{ad-bc}=\l(\frac{-b}{ad-bc}\r)\alpha+\l(\frac{-a}{ad-bc}\r)\alpha\tau
        \end{equation*}
        But $\tau'\in\alpha\Gamma$, which forces $ad-bc=\pm1$. A little algebra now shows that
        \begin{equation*}
            \Im\tau'=\frac{ad-bc}{\l|c\tau+d\r|^2}\l(\Im\tau\r)>0,
        \end{equation*}
        so $ad-bc=1$. Thus $\tau'$ lies in the orbit of $\tau$, as desired. Finally, the corollary follows from Lemma \ref{MS:lem:moduli_space_torus_2}.\qed
    \end{proof}
\end{document}
